Evolution of precopulatory and postcopulatory inbreeding behaviour

### 2016-09-05 ms_pre_post.Rmd
Add introductory paragraph on interaction between different types of inbreeding strategy

---
title: "Evolution of precopulatory and postcopulatory inbreeding behaviour"
author: "A. Bradley Duthie et al."
date: "August 24, 2016"
output:
  pdf_document:
    fig_caption: yes
  html_document: default
  word_document: null
header-includes:
- \usepackage{natbib}
- \usepackage{lineno}
- \linenumbers
- \bibliographystyle{amnatnat}
linestretch: 1
bibliography: ms_pre_post.bib
---

@@

<!--- TODO: PARAGRAGH ON EVOLUTION OF POLYANDRY --->
Critically, evolution of post-copulatory inbreeding avoidance is precluded if females only mate with one male, meaning that evolution of polyandry is intrinsically tied to female inbreeding fertilisation strategy. Although polyandry is commonplace in wild populations, the regularity with which it is observed in the wild remains theoretically puzzling because engaging in polyandry does not necessarily increase the number of offspring that a female produces, meaning that the fitness benefits associated with polyandry are not always clear [@Parker2013; Taylor2014]. It has been hypothesised that females can acheive a net fitness benefit if polyandry provides them with additional opportunities to adjust their inbreeding through copulations with additional males [e.g., @Tregenza2002; @Akcay2007; @Lehtonen2015]. @Duthie showed that selection for polyandry to facilitate inbreeding avoidance is sometimes predicted, but only under highly constrained conditions in which very few males are available during a female's initial mate choice but many males are available during a female's additional mate choice(s), or when expression of polyandry is conditionally expressed based on the degree of inbreeding in a female's initially chosen mate. However, @Duthie assumed that polyandrous females had no control over the assignment of paternity to their offspring. If after engaging in polyandry, females could bias paternity toward non-relatives, then selection for polyandry to avoid inbreeding might be more widely predicted. However, no models quantify the degree to which expression of biased paternity resulting from evolving inbreeding fertilisation strategy can feedback to drive evolution of polyandry in populations of potentially inbreeding females and males with biologically realistic distributions of relatedness.

<!--- TODO: PARAGRAGH ON IDEA THAT RELATIVE COSTS WILL DETERMINE PRE VS POST --->

@@

>>>>

---
title: "Evolution of precopulatory and postcopulatory inbreeding behaviour"
author: "A. Bradley Duthie et al."
date: "August 24, 2016"
output:
  pdf_document:
    fig_caption: yes
  html_document: default
  word_document:
    fig_caption: yes
    pandoc_args:
    - --csl
    - evolution.csl
header-includes:
- \usepackage{natbib}
- \usepackage{lineno}
- \linenumbers
- \bibliographystyle{amnatnat}
linestretch: 1
csl: evolution.csl
bibliography: ms_pre_post.bib
---

@@

<!--- TODO: PARAGRAGH ON EVOLUTION OF POLYANDRY --->
Critically, evolution of post-copulatory inbreeding avoidance is precluded if females only mate with one male, meaning that evolution of polyandry is intrinsically tied to female inbreeding fertilisation strategy. Although polyandry is commonplace in wild populations, the regularity with which it is observed in the wild remains theoretically puzzling because engaging in polyandry does not necessarily increase the number of offspring that a female produces, meaning that the fitness benefits associated with polyandry are not always clear [@Parker2013; @Taylor2014]. It has been hypothesised that females can acheive a net fitness benefit if polyandry provides them with additional opportunities to adjust their inbreeding through copulations with additional males [e.g., @Tregenza2002; @Akcay2007; @Lehtonen2015]. @Duthie showed that selection for polyandry to facilitate inbreeding avoidance is sometimes predicted, but only under highly constrained conditions in which very few males are available during a female's initial mate choice but many males are available during a female's additional mate choice(s), or when expression of polyandry is conditionally expressed based on the degree of inbreeding in a female's initially chosen mate. However, @Duthie assumed that polyandrous females had no control over the assignment of paternity to their offspring. If after engaging in polyandry, females could bias paternity toward non-relatives, then selection for polyandry to avoid inbreeding might be more widely predicted [@Zeh1997]. However, no models quantify the degree to which expression of biased paternity resulting from evolving inbreeding fertilisation strategy can feedback to drive evolution of polyandry in populations of potentially inbreeding females and males with biologically realistic distributions of relatedness.

<!--- TODO: PARAGRAGH ON IDEA THAT RELATIVE COSTS WILL DETERMINE PRE VS POST --->
Evolution of inbreeding fertilisation stratey might increase selection for polyandry, but evolutionary feedbacks between inbreeding fertilisation strategy and polyandry might also be contingent upon evolution of inbreeding mating strategy, thereby leading to complex evolutionary dynamics between inbreeding strategies and polyandry. For example, if females can acheive their desired degree of inbreeding through mate choice alone, then subsequent polyandry and inbreeding fertilisation strategy might be superfluous for increasing female fitness. Alternatively, if females are often unsuccessful at realising their inbreeding mating strategy due to factors such as sexual conflict over mating and resulting male coercion [e.g., @Parker2006], limited kin recognition amongst potential mates [e.g., @Penn2010], or simply the inherent stochasticity associated with mate encounters or expression of mate choice based on inbreeding [e.g., @Kokko2006; @Duthie], then selection on inbreeding fertilisation strategy might occur to reinforce inbreeding mating strategy. In empirical systems where inbreeding depression is severe and inbreeding avoidance is therefore beneficial, expression of inbreeding mating strategy and inbreeding fertilisation strategy have been observed across diverse taxa [e.g., @Gasparini2011; @Tuni2013; @Firman2015; @Fischer2015; @Daniel2015]. However, no models predict *a priori* which of these inbreeding strategies should be observed when inbreeding depression is sufficiently severe to make inbreeding avoidance adaptive.

@@

<!--- The initial evolution of inbreeding fertilisation strategy might be further facilitated if the phenotypic expression of polyandry is caused by continuous genetic variation underlying a female's tendency for engaging in polyandry, as is expected for complex polygenic traits underlying behaviour under the fundamental assumptions of quantitative genetics [@Evans2008]. Under quantitative genetic assumptions, polyandry can therefore be conceptualised as a 'threshold trait', meaning that multiple mating is only realised above some threshold genetic value [@Lynch1998]. Expression of  --->
